Sample-Based Determination of Angular Observables

### 2014-06-24 draft.tex
Move first paragraph of Intro to Abstract

\begin{abstract}
We study means to determine angular observables for a generic angular distribution
of a decay or scattering process. \dots
\end{abstract}

@@

In this letter we study how to obtain a set of angular observables
$\{P_i\}$ that arise in a generic multi-body process without the need
to carry out a likelihood fit of an angular distribution to the
measured events. Instead, we present a method that only relies on
orthogonality of angular functions, and estimation of integrals
by means of Monte Carlo techniques. \fred{Paragraph sounds like abstract}\\

>>>>

\begin{abstract}
In this letter we study how to obtain a set of angular observables
$\{P_i\}$ that arise in a generic multi-body process without the need
to carry out a likelihood fit of an angular distribution to the
measured events. Instead, we present a method that only relies on
orthogonality of angular functions, and estimation of integrals
by means of Monte Carlo techniques.
\end{abstract}

@@
